%-------------------------
% Resume Hardik Singh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\latex}{\LaTeX\xspace}
\newcommand{\tex}{\TeX\xspace}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hardik Singh} & \textbf{Email:} \href{mailto:hardikgaya141@gmail.com}{hardikgaya141@gmail.com} \\
  \textbf{Phone:} +91 6201338470 & \textbf{GitHub:} \href{https://github.com/hardik4555/}{https://github.com/hardik4555/} \\
  \textbf{LinkedIn:} \href{https://www.linkedin.com/in/hardik-singh-441295223/}{https://www.linkedin.com/in/hardik-singh-441295223/}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Indian Institute of Technology (IIT) Patna}{Patna, India}
    {B.S in Mathematics and Computing  \textbf{CPI: 8.13}}{July 2021 - May 2025 (Expected)}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Patna Doon Public School}{Patna, India}
    {All India Senior School Certificate Examination (AISSCE) conducted by CBSE. \textbf{Percentage: 90\%}}{Apr 2020 - Mar 2021}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Accomplishments}
\resumeSubHeadingListStart
  \item Specialist on CodeForces with max rating \href{https://codeforces.com/profile/hardik_alt}{\textbf{1409}}.
  \item 3-star coder on CodeChef with max rating \href{https://www.codechef.com/users/hardikkk09}{\textbf{1591}}.
  \item Secured a global rank of \href{https://codeforces.com/contest/1809/standings/k}{\textbf{1595}} out of \textbf{14541} candidates in Educational Codeforces Round 145 held on 23rd Mar 2023.
  \item Secured a global rank of \href{https://www.codechef.com/rankings/START97C?itemsPerPage=100&order=asc&page=1&sortBy=rank}{\textbf{51}} out of \textbf{3612} candidates in CodeChef's Starters 97.
  \item Secured an All India Rank of \textbf{4555} out of more than \textbf{0.17} million candidates in JEE Advanced 2021.
  \item Scored \textbf{99.43} percentile out of more than \textbf{1.14} million candidates in JEE Mains 2021.
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Weather Application (Using React JS)}{\href{https://github.com/hardik4555/react-weather}{\textbf{Source Code}}}
    {Feb 2023 - Mar 2023}{}
    \resumeItemListStart
      \item Made a weather application which provides important factors like temperature, wind, humidity, and pressure of various cities around the world.
      \item Utilized the {\textbf{OpenWeather API}} for weather details and the {\textbf{GeoDB API}} for information about various cities.
      \item Implemented auto-complete feature enabling users to get data of all cities with a common prefix in their name.
    \resumeItemListEnd
    
  \resumeSubheading
    {Clone of Amazon Homepage (HTML, CSS)}{\href{https://github.com/hardik4555/amazon-website-clone}{\textbf{Source Code}}}
    {June 2022}{}
    \resumeItemListStart
      \item Created a clone of the e-commerce site Amazon using basic HTML and CSS.
    \resumeItemListEnd

    \resumeSubheading
    {Clone of Spotify App (HTML, CSS, Javascript)}{\href{https://github.com/hardik4555/amazon-website-clone}{\textbf{Source Code}}}
    {august 2022}{}
    \resumeItemListStart
      \item Made a clone of music App spotify using basic HTML and CSS for the user interface and adding song functionalities using Javascript.
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills/Relevant coursework}
\resumeSubHeadingListStart
  \item \textbf{Programming/Development Languages:} C/C++, Python, HTML, CSS, JavaScript
  \item \textbf{Competitive Programming:} Have solved over 600 problems on Codeforces and over 300 problems on LeetCode, focusing on various data structures and algorithms.
  \item \textbf{Core Courses:} Algorithms and Data Structures, Discrete Mathematics, Digital Design, Numerical Linear Algebra
  \item \textbf{Mathematics:} Probability and Random Processes, Multivariable Calculus, Linear Algebra, Complex Analysis
\resumeSubHeadingListEnd

\end{document}
